---
title       : Motor Trend Cars
subtitle    : MPG Linear Regretion
author      : Alex Ahumada
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Proposed Model

```{r, echo=FALSE}
library(tables)
library(datasets)
library(xtable)

data(mtcars)

# fit <- lm(formula = mpg ~ factor(am) + factor(cyl) + wt + hp, data = mtcars)
# 
# print( tabular( mpg + 1 ~ 1, data = mtcars  ) )

df <- data.frame(A = c(1.00123, 33.1, 6),
                 B = c(111111, 3333333, 3123.233))
## The following code gives the error
## formal argument "digits" matched by multiple actual arguments
## print(xtable(df, display = c("s","e","e")),
## format.args = list(digits = 3, big.mark = " ", decimal.mark = ","))
## specify digits as argument to xtable instead

print(xtable(df, display = c("s","f","f"), digits = 4),
      format.args = list(big.mark = " ", decimal.mark = ","), type = "html" )

```

--- .class #id 

## Residual Plot

```{r, echo=FALSE}

opar <- par(mfrow = c(2, 2))
plot(fit)
par( opar )

```

--- .class #id 


## User Guide

You have to select a regresor  for MPG and application will show to you:

- Scatterplot in case of variable it continuous
- Boxplot in case of variable it discrete.

Enjoy it!

--- .class #id 

## Executive Summary

This application try to answer specific question regarding the cars's relationship between miles per galon (MPG) and other variables in dataset. For this we have the folowing database:

```
Motor Trend Car Road Tests: The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models)
This aplication show scaterplot graphics and tendence line retulting of applying linear regression to a mtcars dataset 

```

--- .class #id 

## Data Description Table

The field in the data have the following meaning:

  Variable | Description 
  :-------:|:---------------
  mpg      |Miles/(US) gallon        
  cyl      |Number of cylinders      
  disp     |Displacement (cu.in.)   
  hp       |Gross horsepower         
  drat     |Rear axle ratio          
  wt       |Weight (lb/1000)         
  qsec     |1/4 mile time            
  vs       |V/S             
  am       |Transmission (0 = automatic, 1 = manual)
  gear     |Number of forward gears
  carb     |Number of carburetors 

--- .class #id 

## Data Sample

```{r}
head(mtcars)
```
